### 2010-06-28 trunk/paper/IIWAS2010/content/results_discussion.tex
small space saving change
update to conclusion

\subsection{Discussion}

>>>>

We used this top category of each of the terms in the candidate SSQ and
determined the category divergence with the qualified SSQ categories in the QRM
store. We assumed that all of them belong to the same realm or domain (but, it
is different in real time). In the end, we combined the divergence measure and
ranked QRMs based on the relevance score. Table \ref{tbl:ranked_queries}
shows the top ranked queries that belong to the QRMs in store for the above
query.

\begin{tabular}{l | r}
Query & Score\\
\hline
A 1997 Toyota Camry V6 needs what size tires? & 0.91\\ 
What is the tire size for a 1998 Sienna XLE Van? & 0.72\\ 
What is the tire size for a 1996 Infiniti I30 Sedan? & 0.88\\ 
\hline
\end{tabular}

\caption{Top ranked queries and relevance scores}
\label{tbl:ranked_queries}

%\subsection{Discussion}
\section{Conclusion}

In this paper, we proposed a novel question answering system that uses previously answered user queries to answer similar questions using deep web site.  The system uses a guide user to annotate answer paths so folowing users can discover answers to complicated questions.  Each question answer pair is assigned a realm, and new questions are matched to the new question answer pairs. [How do we calculate relam for a candidate query? and NLP]. This question matching strategy assumes that candidate query terms are available in the category corpus. The candidate query's category annotation will fail if the
query terms are not available in the corpus. In addition, classification of a term or n-gram into a category is based on the term frequency distributions in a classified web document. We are working on improving this
approach by using a probabilistic generative approach as used in the Topic
Models\cite{Blei2003latentdirichlet}.

Similarly, the Morpheus ontology building
process needs categorized web pages. As explained in section
\ref{sec:ontology_generators}, the Wikipedia page categories have some
limitations for this purpose. Without supervision, the page categorization is
often a challenging problem, because topics in the pages that belong to a realm
(e.g. automotive) usually overlap. So we are evaluating the applicability of
probabilistic topic models to web page categorization, and automatic
generation of a realm-ontology based on the topics being extracted.
